The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-26 paper.tex
Solved bib conflicts + use Latex special chars

In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior. This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}. A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.

>>>>

In sum, this branch of research suggests that anthropomorphism implies that
people thoughtfully develop a mental model of agents in their environment and
that they make inferences about these agents based on what is familiar to them
-- themselves, humans and human behavior. This understanding builds on a
person's ability to attribute mental states to oneself and others, which is
called \textit{Theory of Mind}~\citep{premack1978does}. A theory of mind for
other agents enables us to attribute intentionality to those agents
\citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this
tendency to thoughtfully anthropomorphize and the engagement in the attribution
of mental states to other humans were recently demonstrated at the brain
level~\citep{cullen2013individual}.
